RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-02-16 jsac.tex
:pencil: Update reference for DCMC capacity

			During backscatter detection, the primary symbols $s[1],\ldots,s[n]$ can be viewed as a spreading code, and the receiver employs \gls{mrc} over $N$ primary blocks.
			The total achievable for nodes with equiprobable inputs is \cite{Wang2014a}

>>>>

			During backscatter detection, the primary symbols $s[1],\ldots,s[N]$ function as a spreading code and the receiver performs \gls{mrc} on $\hat{y}^{\text{\gls{sr}}}[n]$ over $N$ primary blocks.
			This essentially formulates a discrete-input continuous-output memoryless channel and the total backscatter achievable rate is maximized with equiprobable inputs as \cite{Ng2006}
